### 2018-04-27 doc/paper.tex
Updating "failed compensation" table.
This way it includes the two columns needed to get the
answer to full precision.

(I verified this with `de_casteljau._compensated4()` and it
matches the values **exactly** at every step.)
Dropping `2^{38.6}` in favor of exact/compact expression.
Changing `Delta` to `partial`.
Also renaming the "K-fold" section to "operation counts"
and reserving the "K-fold" section for future use.
Adding diagram of the error filtering process.

@@

  \begin{algorithmic}
    \Function{\(\mathtt{res} = \mathtt{CompDeCasteljau}\)}{$\mathbf{b}, s$}
      \State \(n = \texttt{length}(\mathbf{b}) - 1\)
      \State \(\left[r, \rho\right] = \mathtt{TwoSum}(1, -s)\)
      \\
      \For{\(j = 0, \ldots, n\)}
        \State \(b_j^{(n)} = b_j\)
        \State \(\Delta b_j^{(n)} = 0\)
      \EndFor
      \\
      \For{\(k = n - 1, \ldots, 0\)}
        \For{\(j = 0, \ldots, k\)}
          \State \(\left[P_1, \pi_1\right] = \mathtt{TwoProd}\left(
              r, b_j^{(k + 1)}\right)\)
          \State \(\left[P_2, \pi_2\right] = \mathtt{TwoProd}\left(
              s, b_{j + 1}^{(k + 1)}\right)\)
          \State \(\left[b_j^{(k)}, \sigma_3\right] = \mathtt{TwoSum}(
              P_1, P_2)\)
          \State \(w = \pi_1 \oplus \pi_2 \oplus \sigma_3 \oplus
              \left(\rho \otimes b_j^{(k + 1)}\right)\)
          \State \(\Delta b_j^{(k)} = w \oplus \left(s \otimes
              \Delta b_{j + 1}^{(k + 1)}
              \right) \oplus \left(r \otimes \Delta b_j^{(k + 1)}\right)\)
        \EndFor
      \EndFor
      \\
      \State \(\mathtt{res} = b_0^{(0)} \oplus \Delta b_0^{(0)}\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

Consider
\[p(s) = (4s - 3)^3 (8s + 7) = (-189) B_{0, 4}(s) + (-54) B_{1, 4}(s) +
57 B_{2, 4}(s) + (-32) B_{3, 4}(s) + 15 B_{4, 4}(s)\]
at the point \(s = \frac{3}{4} + 800 u\). In exact arithmetic, we
have \(p(s) = 2^{38.6} u^3 + \mathcal{O}\left(u^4\right)\).
However, using the compensated de Casteljau algorithm results in
\(b_0^{(0)} + \Delta b_0^{(0)} = 0\):

\begin{center}
  \begin{tabular}{>{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$}}
    \toprule
    k & j & b_j^{(k)} & \Delta b_j^{(k)} \\
    \midrule
    3 & 0 & -87\frac{3}{4} + 108032u & -32u \\
    3 & 1 & 29\frac{1}{4} + 88768u & 32u \\
    3 & 2 & -9\frac{3}{4} - 71200u & 0 \\
    3 & 3 & 3\frac{1}{4} + 37600u & 0 \\
    \midrule
    2 & 0 & 187200u & -15360000u^2 \\
    2 & 1 & -62408u & 8u - 128000000u^2 \\
    2 & 2 & 20800u & 87040000u^2 \\
    \midrule
    1 & 0 & -6u - 199688192u^2 & \boxed{6u - 99831808u^2} \\
    1 & 1 & -2u + 66568192u^2  & \boxed{2u + 33271808u^2} \\
    \midrule
    0 & 0 & -3u + 7296u^2 & \boxed{3u - 7296u^2} \\
    \bottomrule
  \end{tabular}
\end{center}
This is due to dropped terms: \(\Delta b_0^{(1)}\) drops \(-90112000000u^3\),
\(\Delta b_1^{(1)}\) drops \(172032000000u^3\), \(\Delta b_0^{(0)}\) drops
\(319488000000u^3\) (that's relative to the \textbf{incorrect}
\(\Delta b_j^{(1)}\) terms, if compared to the correct terms there'd also
be a \(u^4\) term dropped).

@@

>>>>

%% H/T: https://tex.stackexchange.com/a/99051/32270
\PassOptionsToPackage{usenames,dvipsnames}{xcolor}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}
\tikzstyle{box} = [
  rectangle, minimum width=0.1\textwidth, minimum height=0.1\textwidth,
  text centered, draw=black]
\tikzstyle{empty-box} = [
  rectangle, minimum width=0.1\textwidth, minimum height=0.1\textwidth,
  text width=0.05\textwidth]
\tikzstyle{empty-box-vert} = [
  rectangle, minimum width=0.1\textwidth, minimum height=0.1\textwidth,
  text centered, text height=0.001\textwidth]
\tikzstyle{line} = [draw, -latex']

@@

  \begin{algorithmic}
    \Function{\(\mathtt{res} = \mathtt{CompDeCasteljau}\)}{$\mathbf{b}, s$}
      \State \(n = \texttt{length}(\mathbf{b}) - 1\)
      \State \(\left[r, \rho\right] = \mathtt{TwoSum}(1, -s)\)
      \\
      \For{\(j = 0, \ldots, n\)}
        \State \(b_j^{(n)} = b_j\)
        \State \(\partial b_j^{(n)} = 0\)
      \EndFor
      \\
      \For{\(k = n - 1, \ldots, 0\)}
        \For{\(j = 0, \ldots, k\)}
          \State \(\left[P_1, \pi_1\right] = \mathtt{TwoProd}\left(
              r, b_j^{(k + 1)}\right)\)
          \State \(\left[P_2, \pi_2\right] = \mathtt{TwoProd}\left(
              s, b_{j + 1}^{(k + 1)}\right)\)
          \State \(\left[b_j^{(k)}, \sigma_3\right] = \mathtt{TwoSum}(
              P_1, P_2)\)
          \State \(w = \pi_1 \oplus \pi_2 \oplus \sigma_3 \oplus
              \left(\rho \otimes b_j^{(k + 1)}\right)\)
          \State \(\partial b_j^{(k)} = w \oplus \left(s \otimes
              \partial b_{j + 1}^{(k + 1)}
              \right) \oplus \left(r \otimes \partial b_j^{(k + 1)}\right)\)
        \EndFor
      \EndFor
      \\
      \State \(\mathtt{res} = b_0^{(0)} \oplus \partial b_0^{(0)}\)
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

Consider
\[p(s) = (4s - 3)^3 (8s + 7) = (-189) B_{0, 4}(s) + (-54) B_{1, 4}(s) +
57 B_{2, 4}(s) + (-32) B_{3, 4}(s) + 15 B_{4, 4}(s)\]
at the point \(s = \frac{3}{4} + 800 u\). In exact arithmetic, we
have \(p(s) = 13(3200u)^3 + \mathcal{O}\left(u^4\right)\).
However, using the compensated de Casteljau algorithm results in
\(b_0^{(0)} + \partial b_0^{(0)} = 0\):

\begin{center}
  \begin{tabular}{>{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$} >{$}c<{$}}
    \toprule
    k & j & b_j^{(k)} & \partial b_j^{(k)} & \partial^2 b_j^{(k)} & \partial^3 b_j^{(k)} \\
    \midrule
    3 & 0 & -87\frac{3}{4} + 108032u & -32u & 0 & 0 \\
    3 & 1 & 29\frac{1}{4} + 88768u & 32u & 0 & 0 \\
    3 & 2 & -9\frac{3}{4} - 71200u & 0 & 0 & 0 \\
    3 & 3 & 3\frac{1}{4} + 37600u & 0 & 0 & 0 \\
    \midrule
    2 & 0 & 187200u & -15360000u^2 & 0 & 0 \\
    2 & 1 & -62408u & 8u - 128000000u^2 & 0 & 0 \\
    2 & 2 & 20800u & 87040000u^2 & 0 & 0 \\
    \midrule
    1 & 0 & -6u - 199688192u^2 & 6u - 99831808u^2 & -90112000000u^3 & 0 \\
    1 & 1 & -2u + 66568192u^2  & 2u + 33271808u^2 & 172032000000u^3 & 0 \\
    \midrule
    0 & 0 & -3u + 7296u^2 & 3u - 7296u^2 & 13 (3200u)^3 + 3048(512u)^4 & 962(128u)^4 \\
    \bottomrule
  \end{tabular}
\end{center}

@@

\begin{center}
\begin{tikzpicture}[node distance = 0.2\textwidth]
    \node [box] (bj) {\(b_j\)};
    \node [box, below of=bj] (bn0) {\(b_j^{(n)}\)};
    \node [box, right of=bn0] (dbn0) {\(\partial b_j^{(n)}\)};
    \node [box, right of=dbn0] (ddbn0) {\(\partial^2 b_j^{(n)}\)};
    \node [box, right of=ddbn0] (dddbn0) {\(\partial^3 b_j^{(n)}\)};
    %%
    \node [box, below of=bn0] (bn1) {\(b_j^{(n - 1)}\)};
    \node [box, below of=dbn0] (dbn1) {\(\partial b_j^{(n - 1)}\)};
    \node [box, below of=ddbn0] (ddbn1) {\(\partial^2 b_j^{(n - 1)}\)};
    \node [box, below of=dddbn0] (dddbn1) {\(\partial^3 b_j^{(n - 1)}\)};
    %%
    \node [box, below of=bn1] (bn2) {\(b_j^{(n - 2)}\)};
    \node [box, below of=dbn1] (dbn2) {\(\partial b_j^{(n - 2)}\)};
    \node [box, below of=ddbn1] (ddbn2) {\(\partial^2 b_j^{(n - 2)}\)};
    \node [box, below of=dddbn1] (dddbn2) {\(\partial^3 b_j^{(n - 2)}\)};
    %%
    \path [line] (bn0) -- node[above] {\(w_1^{(n)}\)} (dbn0);
    \path [line] (dbn0) -- node[above] {\(w_2^{(n)}\)} (ddbn0);
    \path [line] (ddbn0) -- node[above] {\(w_3^{(n)}\)} (dddbn0);
    \node [empty-box, right of=dddbn0] (right0) {\(\cdots\)};
    \path [line] (dddbn0) -- node[above] {\(w_4^{(n)}\)} (right0);
    %%
    \path [line] (bn1) -- node[above] {\(w_1^{(n - 1)}\)} (dbn1);
    \path [line] (dbn1) -- node[above] {\(w_2^{(n - 1)}\)} (ddbn1);
    \path [line] (ddbn1) -- node[above] {\(w_3^{(n - 1)}\)} (dddbn1);
    \node [empty-box, right of=dddbn1] (right1) {\(\cdots\)};
    \path [line] (dddbn1) -- node[above] {\(w_4^{(n - 1)}\)} (right1);
    %%
    \path [line] (bn2) -- node[above] {\(w_1^{(n - 2)}\)} (dbn2);
    \path [line] (dbn2) -- node[above] {\(w_2^{(n - 2)}\)} (ddbn2);
    \path [line] (ddbn2) -- node[above] {\(w_3^{(n - 2)}\)} (dddbn2);
    \node [empty-box, right of=dddbn2] (right2) {\(\cdots\)};
    \path [line] (dddbn2) -- node[above] {\(w_4^{(n - 2)}\)} (right2);
    %%
    \path [line] (bj) -- (bn0);
    \path [line] (bn0) -- node[fill=white] {\(U_n(s)\)} (bn1);
    \path [line] (bn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (bn2);
    \node [empty-box-vert, below of=bn2] (bottom0) {\(\vdots\)};
    \path [line] (bn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom0);
    %%
    \path [line] (dbn0) -- node[fill=white] {\(U_n(s)\)} (dbn1);
    \path [line] (dbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dbn2);
    \node [empty-box-vert, below of=dbn2] (bottom1) {\(\vdots\)};
    \path [line] (dbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom1);
    %%
    \path [line] (ddbn0) -- node[fill=white] {\(U_n(s)\)} (ddbn1);
    \path [line] (ddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (ddbn2);
    \node [empty-box-vert, below of=ddbn2] (bottom2) {\(\vdots\)};
    \path [line] (ddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom2);
    %%
    \path [line] (dddbn0) -- node[fill=white] {\(U_n(s)\)} (dddbn1);
    \path [line] (dddbn1) -- node[fill=white] {\(U_{n - 1}(s)\)} (dddbn2);
    \node [empty-box-vert, below of=dddbn2] (bottom3) {\(\vdots\)};
    \path [line] (dddbn2) -- node[fill=white] {\(U_{n - 2}(s)\)} (bottom3);
\end{tikzpicture}
\end{center}

\subsection{Operation Counts}
